More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-12-20 2016-Weak-FH-Bisim/WeakBisim.tex
todos de la reunion
yet lemma 5

Notes de reunion 24 Sept

@@

We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}	\models		\openrule
    {
       \set{\beta}_p,\Pred_p,\Post_p   }
         {\ostate{s_p^1} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred_p}\!\!',  
				{\Post_p}\!\!'}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \left\{
		Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
\right.$\\
Else $Q$ does not move and \\
$P\models{\openrule
			{
				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred_p},  
				{\Post_p}}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $
such that  $\Pred_p \iff {\Pred_p}\!\!'
		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post_p={\Post_p}\!\!'\uplus 
		{\Post_p}\!\!''$ where ${{\Post_p}\!\!''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.

@@

\item Similarly, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta},\Pred,\Post }
         {\ostate{s} \OTarrow {\alpha} \ostate{s'}}$\\
We obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	 \left\{
  \begin{array}{l}
		%\[
		Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{s_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{s_l'^{\,l\in L_Q}}}
		}\\%\]
	or\\
		\openrule
         {
          (j\mapsto\tau)^{j\in L\cap\Holes(Q)},\True,\Id(s_{pl}^{l\in L_Q})}
         {s_{pl}^{l\in L_Q} \OTarrow {\tau} s_{pl}^{l\in L_Q}}

\end{array}
\right.	
		$
such that  $\Pred \iff {\Pred}\,'
		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post={\Post}\,'\uplus 
		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post$ over variables of $\Leaves(Q)$.
\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
Considering each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$, the set of open transition that moves at each time, i.e,  the open transition $\symb{OT}_p$ in the form:
\begin{mathpar}
Q\models{\openrule
			{
				(\beta_p)_j^{J_p}, {\Pred_p},  
				{\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]

By rule (\WTTrois)  we can conclude that for each $p\in S$ we have:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
such that $\gamma_p = \vis{\beta_p}$.\\
\TODO{maybe it is better to use $\gamma_p=[\beta_p]$}\\

>>>>

TODOs du 19 decembre

- TROUVER UN EXEMPLE ET LE METTRE DANS L ARTICLE

- enlever 5.2 et citer avocs

- ajouter des proof sketch dans le papier

- def 11 point 2:
A, Pred, Post
-----------   in T
s->s'
et A(j)=tau
implies blablabla

- adopter la def semantique d ot pour la bisim

OLD OLD OLD (check)
Notes de reunion 24 Sept

@@

We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}	\models		\openrule
    {
       \set{\beta}_p,\Pred_p,\Post_p   }
         {\ostate{s_p^1} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred_p}\!\!',  
				{\Post_p}\!\!'}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$\\
Else $Q$ does not move and \\
$P\models{\openrule
			{
				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred_p},  
				{\Post_p}}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $
such that  $\Pred_p \iff {\Pred_p}\!\!'
		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post_p={\Post_p}\!\!'\uplus 
		{\Post_p}\!\!''$ where ${{\Post_p}\!\!''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.

@@

\item Similarly, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta},\Pred,\Post }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}\\%\]
$
Else $Q$ does not move we  \\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
				\ostate{t_l'^{\,l\in L_Q}}$
such that  $\Pred \iff {\Pred}\,'
		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post={\Post}\,'\uplus 
		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post$ over variables of $\Leaves(Q)$.
\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1 and 2 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}

\TODO{We will add side conditions ?? }\\
Concerning $Q$ if it moves, for each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$ in the form:
\begin{mathpar}
Q\models{\openrule
			{
				(\beta_p)_j^{J_p}, {\Pred_p},  
				{\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]

\end{mathpar}
By rule (\WTTrois)  we can conclude that  we have:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
such that $\gamma_p = \vis{\beta_p}$.
\TODO{maybe it is better to use $\gamma_p=[\beta_p]$}\\
